Gaia's constraints on the very massive (initially $\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-07-01 VFTS682_APJL.tex
acknowledgements
update to fig caption and text

Figure~\ref{fig:main} shows the projected motion of VFTS682 relative to R136 on the
sky. \todo{fix colors} The dashed circle shows the location of the cluster, and the red
(cyan) arrow shows the relative proper motion from \emph{Gaia} DR2
(HST). The lighter arrows show the uncertainty on the direction of
motion due to the large uncertainties. The length of each arrow is proportional to
the speed of the star, and dashed prolungations show the possible
region of origin assuming an age of $1.0\pm0.2$\,Myr
\citep[][]{schneider:18}. This figure illustrates that R136 is clearly
the most likely origin of the star, although the large error bars
prevent a robust identification.

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.48\textwidth]{./figures/main_plot_good_gaia_only}  
  \caption{The red solid arrow indicates the proper motion of VFTS682 
    relative to the region from \emph{Gaia} DR2, starting from the present day position of
    the star. The yellow arrows indicate the possible
    directions of projected motion within the \emph{Gaia} DR2 errors, and are extended
    backwards (dashed) to illustrate the uncertainty on the origin of the
    star. The length of the prolongations is proportional to the relative proper motion
    times the age of VFTS682 \citep[$1.0\pm0.2$\,Myr,][]{schneider:18}.
    % \todo{load color picture on background? Fig with HST data
    % available, but confusing...}
  }

@@

 \begin{acknowledgements}
   \small
   We are grateful to M.\,C.\,Ramirez-Tannus, S.~N.~Shore, and S.\,Torres
   % and C.\,J.\,Evans
   for help and discussions, European Unions Horizon 2020 research and innovation programme from the European Research Council (ERC), Grant agreement No. 715063 [SdM], the NRC-Canada Plaskett Fellowship [VHB].

>>>>

Figure~\ref{fig:main} shows the projected motion of VFTS682 relative to R136 on the
sky. We also show VFTS16 and VFTS72 for completeness
\citep[see][]{lennon:18}. The thick cyan arrows are proportional to
the relative proper motion from \emph{Gaia} DR2, and the yellow thick
line illustrates the relative proper motion from HST. The error cone
on the direction of motion is illustrated by the corresponding
prolongation in the direction opposite to the motion, and we also show
the most likely origin of the stars accounting for their apparent age.
This figure illustrates that R136 is the most likely origin of these stars, although the large error bars
prevent a robust identification for VFTS682, and there is some tension
between the apparent age and the present day distance from the cluster
core for VFTS16 and VFTS72 \citep[][]{lennon:18}.

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.48\textwidth]{./figures/Figure2_paper_vfts682_hst}  
  \caption{The thick cyan arrows indicate proper motions relative R136 (blue
    circle) from \emph{Gaia} DR2, multiplied by 1\,Myr. The prolongations in the opposite
    direction are proportional to the apparent ages of the stars, and
    the thin cyan lines illustrate the error cone. The yellow arrow
    indicates the HST proper motion of VFTS682, with the relative
    error cone and prolongation proportional to its apparent age.
    }

@@

 \begin{acknowledgements}
   \small
   We are grateful to J.~Heyl, M.\,C.\,Ramirez-Tannus, S.~N.~Shore, and S.\,Torres
   % and C.\,J.\,Evans
   for help and discussions, European Unions Horizon 2020 research and innovation programme from the European Research Council (ERC), Grant agreement No. 715063 [SdM], the NRC-Canada Plaskett Fellowship [VHB].
